### 2021-03-20 presentation/1_setting.tex
copy corrected system diagram
Fix presentation typos

\I Estimation of Multiple-input multiple-output (MIMO) systems results in high complexity, due to a large number of antennae.

\I Problem (a): How to reconstruct the channel with fewer measurements?

\I Problem (b): How to generate precoders and combiners?
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Channel model and beamforming}
{
\I Given MIMO channel representation \m {\M {H} \in \NC \MB {C} ^{N_H \D N_H}} with uniform linear array, having \m {L} paths, with hybrid beamforming.

@@

\I Tx: Digital precoder \m {\M {F}_B \in \NC \MB {C} ^{N_R \D N_{B,t}}}
\I Tx: Analog precoder \m {\NC \M {F}_R \in \NC \MB {C} ^{N_H \D N_R}}

\I Rx: Digital combiner \m {\M {W}_B \in \NC \MB {C} ^{N_R \D N_H}}
\I Rx: Analog combiner \m {\M {W}_R \in \NC \MB {C} ^{N_{B,r} \D N_R}}

\I Magnitude constraint \m {\Nm {\M {F}_{R,\SB {n_H, n_R}}} = 1}, \m {\Nm {\M {W}_{R,\SB {n_H, n_R}}} = 1}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Cast to Linear System}
{
\I We have \m {\M {Y} =\M {W}_B \M {W}_R \RB {\M {H} \M {F}_R \M {F}_B +\M {Z}}}
\I Introduce the DFT matrix \m {\M {K} \in \NC \MB {C} ^{N_H \D N_H}}, and write
\Disp {
\NC \V {y}
:= \NC \Rm {vec} \SB {\M {Y}},
\Q \M {P}
:= \RB {\M {F}_B^\Tr \M {F}_R^\Tr \m {K}^\ast} \otimes \RB {\M {W}_B \M {W}_R \M {K}}, \NR
\NC \V {g}
:= \NC \Rm {vec} \SB {\M {K}^\Adj \M {H} \M {K}},
\Q \V {z}
:= \Rm {vec} \SB {\M {W}_B \M {W}_R \M {Z}} \NR
}
\I We have an underdetermined system \m {\V {y} =\M {P} \V {g} +\V {z}}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Problem Description}
{
\I Problem (a): How to recover \m {\M {H}} with knowledge of \m {\M {Y}}?

@@

\I Can we find a basis on which \m {\V {g}} is likely to be sparse?
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Literature review}
{
\I Bajwa, Haupt, Sayeed, and Nowak (2010): MIMO, linear invariant system, using Dantzig Selector (DS)

@@

\I Alkhateeb, Leus, and Heath (2015): single path mm wave, all phase shifter beamforming, using Orthogonal Matching Pursuit (OMP)

\I Lee, Lee, and Yong (2016): MIMO mm wave, hybrid beamforming, using Orthogonal Matching Pursuit (OMP)
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Contribution}
{
\I Due to the constraint of hybrid beamforming, designs for fully digital beamforming on sensing matrix might not directly work.

\I We propose a low complexity random generation of beamforming matrices, and justify that it may serve as the sensing matrix for DS.

>>>>

\I Consider a multiple-input multiple-output (MIMO) system with hybrid structure, so we have fewer RF chains than the antennas

\I Problem (a): Can we estimate the channel with fewer measurements?

\I Problem (b): What precoders and combiners help the estimation?
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Channel model and beamforming}
{
\I Given MIMO channel representation \m {\M {H} \in \NC \MB {C} ^{N_H \D N_H}} with uniform linear array, having \m {L} paths, with hybrid beamforming.

@@

\I Tx: Digital precoder \m {\M {F}_B \in \NC \MB {C} ^{N_{B,t} \D N_{B,t}}}
\I Tx: Analog precoder \m {\NC \M {F}_R \in \NC \MB {C} ^{N_H \D N_{B,t}}}

\I Rx: Digital combiner \m {\M {W}_B \in \NC \MB {C} ^{N_{B,r} \D N_H}}
\I Rx: Analog combiner \m {\M {W}_R \in \NC \MB {C} ^{N_{B,r} \D N_{B,r}}}

\I Magnitude constraint \m {\Nm {\M {F}_{R,\SB {n_H, n_{R,t}}}} = 1}, \m {\Nm {\M {W}_{R,\SB {n_H, n_{R,r}}}} = 1}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Cast to Linear System}
{
\I We have \m {\M {Y} =\M {W}_B \M {W}_R \RB {\M {H} \M {F}_R \M {F}_B +\M {Z}}}
\I Introduce the DFT matrix \m {\M {K} \in \NC \MB {C} ^{N_H \D N_H}}, and write
\Disp {
\NC \V {y}
:= \NC \Rm {vec} \SB {\M {Y}},
\Q \M {P}
:= \RB {\M {F}_B^\Tr \M {F}_R^\Tr \m {K}^\ast} \otimes \RB {\M {W}_B \M {W}_R \M {K}}, \NR
\NC \V {g}
:= \NC \Rm {vec} \SB {\M {K}^\Adj \M {H} \M {K}},
\Q \V {z}
:= \Rm {vec} \SB {\M {W}_B \M {W}_R \M {Z}} \NR
}
\I We have an underdetermined system \m {\V {y} =\M {P} \V {g} +\V {z}}
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Problem Description}
{
\I Problem (a): How to recover \m {\M {H}} with knowledge of \m {\M {Y}}?

@@

\I Can we find a basis on which \m {\V {g}} is likely to be sparse?
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Literature review}
{
\I Bajwa, Haupt, Sayeed, and Nowak (2010): MIMO, no beamforming, linear invariant system, using Dantzig Selector (DS)

@@

\I Alkhateeb, Leus, and Heath (2015): single path mm wave, analog beamforming, using Orthogonal Matching Pursuit (OMP)

\I Lee, Lee, and Yong (2016): MIMO mm wave, hybrid beamforming, using Orthogonal Matching Pursuit (OMP)
}
% XXX % % XXX % % XXX % % XXX % % XXX % % XXX %
\Frame {Contribution}
{
\I Due to the constraint of hybrid beamforming, sensing matrix designs for fully digital beamforming does not directly work.

\I We propose a low complexity, i.i.d.\ random beamforming matrices, and justify that it may serve as the sensing matrix for DS.

### 2021-03-20 presentation/4_conclusion.tex
Fix presentation typos

\Frame {Conclusion}
{
\I We estimate MIMO mm-Wave channel \m {\M {H}} by using a modified DS.

@@

\I We analyze the error norm of DS in terms of \m {N_H}, \m {N_B}, and \m{L}, and approximate the asymptotic failure probability.

>>>>

\Frame {Conclusion}
{
\I We estimate MIMO mm wave channel \m {\M {H}} by using a modified DS.

@@

\I We analyze the error norm of DS in terms of \m {N_H}, \m {N_{B,t}}, \m {N_{B,r}}, and \m{L}, and approximate the asymptotic failure probability.

### 2021-03-20 treatise-context/1_introduction.tex
Fix presentation typos

Some scholars applied least absolute shrinkage and selection operator (Lasso) instead.
In fact, it can be shown that Lasso and DS have similar behavior \cite [AsR10].
Lian, Liu and Lau applied Lasso on MIMO with an analog combiner \cite [LLL17].
Destino, Juntti, and Nagaraj used an adaptive Lasso \cite [DJN15], in which they jointly optimize the sensing matrix and pilot vectors.
Vlachos, Alexandropoulos, and Thompson \cite [VAT19] used Lasso on hybrid beamforming with an additional random spatial sampling device.

@@

OMP has since been commonly used for channel estimation.
Alkhateeb, Leus, and Heath Jr.\ \cite [ALH15] examined the trade-off between number of measurement and accuracy for an all-phase-shifter beamforming matrix based on nonuniform fixed set of angles.
Hu, Wang, and He \cite [HWH13] applied OMP to estimate path delay of OFDM subcarriers.
Lee, Gil, and Lee \cite [LGL16] considered a hybrid system, where the hybrid beamforming matrix serves as sensing matrix.
Gao, Dai, and Wang proposed a variant of OMP which there is the assumption of spatially common sparsity \cite [GDW15].

@@

In this treatise, we consider a hybrid structure with a uniform linear array with both precoders and combiners on each side.
In chapter 2, we plan to generate random beamforming matrices, and use DS to estimate the channel in the space frequency domain.
Because of the hybrid structure, here it is not possible to generate the sensing matrix by i.i.d.\ entries, which requires a fully digital structure.
But in chapter 3, we shall see that in our proposal, the effective sensing matrix has RIP for high probability, which may serve as the sensing matrix for DS,
and we give a quantitative bound (which holds for high probability) on the expected error norm.
In chapter 4, numerical results show that DS is superior to other methods for our problem.
Since DS is more accurate, it can be used when the sample is less sufficient and the noise level is higher, where it might be the case that only DS can recover successfully.
Considering its higher complexity, we remark that it can be cast as a linear program, and the basis pursuit denoising form may be used.

@@

Our work is also an improvement to Bajwa et.\ al.\ \cite [BHS10].
First, while their method takes many time slices, for our case a few time slices suffice, since the channel is time independent.
Second, with the further constraint of hybrid beamforming, it is unclear whether their guarantee theorem for recovery is still valid.
Third, generating random sequences can lead to high complexity \cite [LGL16].

>>>>

Some scholars applied least absolute shrinkage and selection operator (Lasso) instead.
In fact, it can be shown that Lasso and DS have similar behavior \cite [AsR10].
Lian, Liu and Lau applied Lasso on MIMO with an analog combiner \cite [LLL17].
Destino, Juntti, and Nagaraj used an adaptive Lasso \cite [DJN15], and Vlachos, Alexandropoulos, and Thompson \cite [VAT19] used Lasso on hybrid beamforming with an additional random spatial sampling device.
Both Destino et al and Vlachos et al optimize formulate an algorithm to jointly find the channel and the sensing matrix, which can result in high complexity.

@@

OMP has since been commonly used for channel estimation.
Alkhateeb, Leus, and Heath Jr.\ \cite [ALH15] examined the trade-off between number of measurement and accuracy for an all-phase-shifter beamforming matrix based on nonuniform fixed set of angles.
Hu, Wang, and He \cite [HWH13] applied OMP to estimate path delay of OFDM subcarriers.
Lee, Gil, and Lee \cite [LGL16] considered a hybrid system, where the hybrid beamforming matrix serves as sensing matrix;
the analog stage is a Fourier matrix, and the digital stage consists of a collection of columns vectors of a unitary matrix.
Gao, Dai, and Wang proposed a variant of OMP which there is the assumption of spatially common sparsity \cite [GDW15].

@@

In this treatise, we consider a hybrid structure with a uniform linear array with both precoders and combiners on each side.
In chapter 2, we plan to generate random beamforming matrices, and use DS to estimate the channel in the space frequency domain.
To the best of our knowledge, the sensing matrix with i.i.d.\ entries in both analog and digital stages has not been discussed on the literature.
In chapter 3, we shall see that in our proposal, the effective sensing matrix has RIP for high probability, which may serve as the sensing matrix for DS,
and we give a quantitative bound (which holds for high probability) on the expected error norm.
In chapter 4, numerical results show that DS is superior to other methods for our problem.
Since DS is more accurate, it can be used when the sample is less sufficient and the noise level is higher, where it might be the case that only DS can recover successfully.
Considering its higher complexity, we remark that it can be cast as a linear program, and the basis pursuit denoising form may be used.

@@

Our work is also an improvement to Bajwa et.\ al.\ \cite [BHS10].
First, while their method takes many time slices, for our case a few time slices suffice, since the channel is time independent.
Second, with the further constraint of hybrid beamforming, the channel matrix is downsampled, it is unclear whether their guarantee for successful signal recovery is still valid.
Third, generating random sequences can lead to high complexity \cite [LGL16], and we instead use random beamforming matrices.

### 2021-03-20 treatise-pdflatex/1_introduction.tex
Fix presentation typos

Some scholars applied least absolute shrinkage and selection operator (Lasso) instead.
In fact, it can be shown that Lasso and DS have similar behavior \cite {AsR10}.
Lian, Liu and Lau applied Lasso on MIMO with an analog combiner \cite {LLL17}.
Destino, Juntti, and Nagaraj used an adaptive Lasso \cite {DJN15}, in which they jointly optimize the sensing matrix and pilot vectors.
Vlachos, Alexandropoulos, and Thompson \cite {VAT19} used Lasso on hybrid beamforming with an additional random spatial sampling device.

@@

OMP has since been commonly used for channel estimation.
Alkhateeb, Leus, and Heath Jr.\ \cite {ALH15} examined the trade-off between number of measurement and accuracy for an all-phase-shifter beamforming matrix based on nonuniform fixed set of angles.
Hu, Wang, and He \cite {HWH13} applied OMP to estimate path delay of OFDM subcarriers.
Lee, Gil, and Lee \cite {LGL16} considered a hybrid system, where the hybrid beamforming matrix serves as sensing matrix.
Gao, Dai, and Wang proposed a variant of OMP which there is the assumption of spatially common sparsity \cite {GDW15}.

@@

Our work is also an improvement to Bajwa et.\ al.\ \cite {BHS10}.
First, while their method takes many time slices, for our case a few time slices suffice, since the channel is time independent.
Second, with the further constraint of hybrid beamforming, it is unclear whether their guarantee theorem for recovery is still valid.
Third, generating random sequences can lead to high complexity \cite {LGL16}.

>>>>

Some scholars applied least absolute shrinkage and selection operator (Lasso) instead.
In fact, it can be shown that Lasso and DS have similar behavior \cite {AsR10}.
Lian, Liu and Lau applied Lasso on MIMO with an analog combiner \cite {LLL17}.
Destino, Juntti, and Nagaraj used an adaptive Lasso \cite {DJN15}, and Vlachos, Alexandropoulos, and Thompson \cite {VAT19} used Lasso on hybrid beamforming with an additional random spatial sampling device.
Both Destino et al and Vlachos et al optimize formulate an algorithm to jointly find the channel and the sensing matrix, which can result in high complexity.

@@

OMP has since been commonly used for channel estimation.
Alkhateeb, Leus, and Heath Jr.\ \cite {ALH15} examined the trade-off between number of measurement and accuracy for an all-phase-shifter beamforming matrix based on nonuniform fixed set of angles.
Hu, Wang, and He \cite {HWH13} applied OMP to estimate path delay of OFDM subcarriers.
Lee, Gil, and Lee \cite {LGL16} considered a hybrid system, where the hybrid beamforming matrix serves as sensing matrix;
the analog stage is a Fourier matrix, and the digital stage consists of a collection of columns vectors of a unitary matrix.
Gao, Dai, and Wang proposed a variant of OMP which there is the assumption of spatially common sparsity \cite {GDW15}.

@@

Our work is also an improvement to Bajwa et.\ al.\ \cite {BHS10}.
First, while their method takes many time slices, for our case a few time slices suffice, since the channel is time independent.
Second, with the further constraint of hybrid beamforming, the channel matrix is downsampled, it is unclear whether their guarantee for successful signal recovery is still valid.
Third, generating random sequences can lead to high complexity \cite {LGL16}, and we instead use random beamforming matrices.
